Fission product decay chain equilibria in \zirconia

### 2019-03-08 manuscript.tex
Add Mark corrections

Nuclear fuel claddings have unique materials challenges owing to the highly active environment in which they operate and the creation of unstable isotopes. Corrosive species in the pin such as iodine, produced directly as a result of uranium fission are known to play a role in SCC \cite{Sidky1998, Fregonese1998, iodinezrmetal}. However, iodine nuclei produced from fission are unstable. Fission of uranium produces iodine precursors, mainly unstable isotopes of tellurium. Both iodine and tellurium are relatively common fission products, with combined independent yields from thermal fission of U$_{235}$ above 5\% \cite{kennett1956mass, iodine129fissionyield, imanishi1976independent, iaeafissionyield, iodine132, amiel1975odd}. In addition, xenon and caesium are also common fission products, as shown in Figure \ref{fig:fissionyield}, with fission product masses firmly within the heavy nuclide peak of uranium and plutonium fission product distribution curves.    \\

Previous work on defect equilibria in \zirconia\ considered the internal oxide layer's effectiveness as a barrier to iodine \cite{kenichiodine2018}. It was found that the tetragonal phase of \zirconia\ is a better barrier to iodine ingress than monoclinic \zirconia , especially at higher oxygen partial pressures. It is also established that tetragonal \zirconia\ will always be present on the inner surface of the cladding in significant quantities because it is self-stabilised by the stresses imposed as the oxide grows into the zirconium metal, in addition to compressive residual stresses induced by radiation damage \cite{causey2005review}. The iodine defect study, however, only informs us about one part of the SCC process. For a more holistic understanding, the life cycle of the iodine must also be taken into account.     \\

@@

Nuclei produced during fission are typically neutron-rich, resulting in decay modes such as $\beta-$ or neutron emission. In the case of tellurium nuclei, most decay into iodine, which then decays into xenon with different half-lives depending on the isotope. Several of these isotopes' fission yield and decay data are shown in Table \ref{table:decaydata}. The decay chain continues with xenon nuclei decaying into caesium, many isotopes of which have half lives measured in years. At this point, conventional power reactor fuel is retired long before a significant proportion of the caesium decays into barium. For this reason we only consider the elements tellurium through caesium in this study. \\

The majority of thermal fission events occur in the outer rim of a fuel pellet. Given a fission product penetration depth of up to 8 $\mu$m in \zirconia\ \cite{degueldre2001behaviour}, a large proportion of fission products implant within the oxide. It has also been observed in PCI failures that there is a time delay on the order of 10 minutes between the power ramping of the reactor and the subsequent breach of the cladding \cite{bergenlid1980experimental, wood1983effects, pankaskie1981mechanistic}. This time delay is in line with the half-lives of many Te and I isotopes (Table \ref{table:decaydata}) such that significant proportions of these isotopes will decay during this time delay, hinting that these phenomena could be related. \\
%In addition, it is known that irradiated cladding containing fresh fuel does not crack when power ramped  \cite{wood1983effects}. \\

@@

Calculations were performed using the CASTEP 8.0 density functional theory (DFT) based code \cite{Clark2005}. Ultra-soft pseudo-potentials with a cut-off energy of 600 eV were employed. The Perdew, Burke and Ernzerhof (PBE) \cite{Perdew1996} parameterisation of the generalised gradient approximation (GGA) was used to describe the exchange correlation functional. A Monkhorst-Pack sampling scheme \cite{Monkhorst1976} was used for Brillouin zone integration, with a minimum \emph{k}-point separation of 0.09 \r{A}\textsuperscript{-1}. The Pulay method for density mixing \cite{Pulay1980} was used to improve simulation convergence. \\

@@

Tellurium on an oxygen site adopts a 0 charge state, which while not obvious (it may be expected to act like oxygen, also a group 6 element), can be reasoned when considering chemical behaviour. Oxygen on its native site will readily adopt a charge state of -2. Tellurium on the other hand, exhibits more metallic behaviour, preferring to get oxidised itself. However, the \ch{V_{O}^{**}} site is highly reducing, and will counter the tellurium ion's proclivity to oxidise. The overall effect on tellurium in this case is to maintain its original electronic structure. Finally, when the tellurium concentration is increased to $10^{-3}$ parts/fu, greater occupancy on the zirconium site is predicted above oxygen pressures of $10^{-17}$ atm, forming the defect \ch{Te_{Zr}^{'''}}. This corresponds to a tellurium charge state of +1. While we would expect an even more positive charge state for tellurium, in this case it is the dominant negative defect by an order of magnitude and is necessary to charge compensate positive hole and \ch{Te_{O}^{**}} defects. \\

In terms of defect volume, \ch{Te_{O}^{**}} has a slightly positive volume of 2.74 \r{A}$^{3}$. This is quite large for a positively charged defect (\ch{V_{O}^{**}} has a defect volume of -40.45 \r{A}$^{3}$), very likely due to the large size of the tellurium atom itself. When tellurium occupies the zirconium site, the resulting \ch{Te_{Zr}^{'''}} has a defect volume of 59.93 \r{A}$^{3}$. While this is lower than the defect volume of \ch{V_{Zr}^{''''}} (88.93 \r{A}$^{3}$)

@@

Iodine was previously predicted in Brouwer diagrams (Figure \ref{figure:tikzbrouwerconctet} to produce the defects \ch{I_{O}^{*}} and \ch{I_{Zr}^{'''}} at low and high oxygen pressures respectively. Since the extrinsic defect site is similar for tellurium defects over most oxygen pressures, $\beta$- decay of tellurium could have directly produced these iodine defects without requiring a change of site. Thus, \ch{Te_{O}^{**}} would decay and produce \ch{I_{O}^{*}} with a defect volume of 29.90 \r{A}$^{3}$, and \ch{Te_{Zr}^{'''}} would decay and produce \ch{I_{Zr}^{'''}} with a defect volume of 87.07 \r{A}$^{3}$. At the oxygen site, this means a defect volume change from 2.74 to 29.90 \r{A}$^{3}$. This increase is in large part due to the change in charge state from 0 to -1, as the ions are of similar size otherwise. \\

Similarly at the zirconium site, the defect volume changes from 59.93 to 87.07 \r{A}$^{3}$. Both of these are relatively large increases in defect volume and will come with an increase in lattice stress in the immediate vicinity of the defect, especially if highly constrained. Of course, this  process will take place continuously over time as tellurium atoms decay, with half-lives ranging from seconds to hours depending on the isotope. It is of note however, that PCI failures tend to occur after power ramps with a time delay, even up to an hour after the transient. While not conclusive, this may hint at a mechanism involving decay processes.

@@

Brouwer diagrams for xenon defects are shown in Figure \ref{figure:xenonbrouwer}. At a xenon concentration of $10^{-5}$ parts/fu \zirconia , the dominant xenon defect is \ch{Xe_{O}^{**}} at low oxygen pressures, and a combination of \ch{Xe_{O}^{**}}, \ch{Xe_{Zr}^{''''}} and \ch{Xe_{Zr}^{'''}} at stoichiometry ($10^{-9}$ atm) and higher. At a higher xenon concentration of $10^{-3}$ parts/fu \zirconia , \ch{Xe_{O}^{**}} becomes the dominant defect over a greater oxygen pressure range, from $10^{-30}$ to $10^{-5}$ atm, with \ch{Xe_{Zr}^{''''}} also present in high concentrations at oxygen pressures above $10^{-20}$ atm. As a noble gas, it is expected that xenon in a 0 charge state (\ch{Xe_{O}^{**}} and \ch{Xe_{Zr}^{''''}}) will be prevalent since the full electronic shell provides a stable configuration. \\

@@

The defect volumes of \ch{Cs_{O}^{**}} and \ch{Cs_{Zr}^{'''}} were 4.38 and 90.37 \r{A}$^{3}$ respectively, less than the Xe defects on the same site. This is consistent with the fact that Cs has a much smaller first ionisation energy than Xe, therefore presenting a smaller energy barrier to reducing it's size on either site to improve lattice fit. Because of this, we do not expect further stresses being imposed on the lattice after Xe decays to Cs. We therefore consider that only Te, I and Xe will be significant in this mechanism, as the only contribution to lattice stresses due to Cs would have occurred through direct implantation after fission.

@@

As fission products proceed down the decay chain from Te to Xe, the defects they produce in \zirconia\ have progressively larger volumes. The change in defect volume when \ch{Te_{Zr}^{'''}} decays and produces \ch{I_{Zr}^{'''}} is +27.14 \r{A}$^{3}$. This then decays and produces the defect \ch{Xe_{Zr}^{''''}}, which leads to an even larger change in defect volume of +28.43 \r{A}$^{3}$. Similarly, at the oxygen site, \ch{Te_{O}^{**}} decays to produce \ch{I_{O}^{*}}, with a resulting defect volume change of +27.16 \r{A}$^{3}$. The lattice mismatch of these defects in \zirconia\ will generate stresses and promote crack formation, exposing Zr metal. If enough fission products are implanted simultaneously, the rate of crack formation may become faster than new passivating oxide can be produced, and typical I-SCC mechanisms will take over to failure. This process may be a contributing factor to fuel cladding failures observed after a power ramp, with reported time delays between ramp and failure aligning with the decay rate of Te and I isotopes.

@@

@@

		[width=8.22cm, xlabel={\ch{log_{10}}($p_{O_{2}}$) (atm)}, ylabel={\ch{log_{10}}([D]) (per f.u.)}, ymin=-10, ymax=0, xmin=-35, xmax=0, legend style={{draw=}, at={(0.30,1.47)}, anchor=north west, legend columns=3, nodes={scale=0.75, transform shape}}]

@@

         \addplot[no marks, draw=yellow!75!blue] table [x=pO2, y=VM{-3},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{V_{Zr}^{'''}}};

@@

         \addplot[no marks, draw=red!60!yellow] table [x=pO2, y=Oi{-2},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{O_{i}^{''}}};
         \addplot[no marks, draw=red!50!yellow] table [x=pO2, y=Oi{-1},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{O_{i}^{'}}};
         \addplot[no marks, draw=red!40!yellow] table [x=pO2, y=Oi{0},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{O_{i}^{x}}};

@@

         \addplot[no marks, dashed, draw=red!70!black] table [x=pO2, y=Tei{0},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{Te_{i}^{x}}};
         \addplot[no marks, dashed, draw=red!50!black] table [x=pO2, y=Tei{-1},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{Te_{i}^{'}}};
        \addplot[no marks, dashed, draw=purple] table [x=pO2, y=Tei{1},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{Te_{i}^{\textperiodcentered}}};

@@

        \addplot[no marks, dashed, draw=black] table [x=pO2, y=TesubO{3},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{Te_{O}^{\textperiodcentered\textperiodcentered\textperiodcentered}}};

@@

         \addplot[no marks, dashed, draw=pink] table [x=pO2, y=TesubZr{-4},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{Te_{Zr}^{''''}}};
         \addplot[no marks, dashed, draw=purple] table [x=pO2, y=TesubZr{-5},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{Te_{Zr}^{'''''}}};

@@

        \addplot[no marks, dashed, draw=red!70!black] table [x=pO2, y=Tei{0},]{dat/te_tet_10-3.dat}; 
        \addplot[no marks, dashed, draw=red!50!black] table [x=pO2, y=Tei{-1},]{dat/te_tet_10-3.dat}; 
        \addplot[no marks, dashed, draw=purple] table [x=pO2, y=Tei{1},]{dat/te_tet_10-3.dat}; 

@@

        \addplot[no marks, dashed, draw=black] table [x=pO2, y=TesubO{3},]{dat/te_tet_10-3.dat}; 

@@

        \addplot[no marks, dashed, draw=pink] table [x=pO2, y=TesubZr{-4},]{dat/te_tet_10-3.dat}; 
        \addplot[no marks, dashed, draw=purple] table [x=pO2, y=TesubZr{-5},]{dat/te_tet_10-3.dat}; 

@@

		\caption{Tetragonal phase Brouwer diagrams of point defects at tellurium concentrations of a) $10^{-5}$ and b) $10^{-3}$, at a temperature of 1500 K. Space charge = 0}

@@

        \addplot[no marks, dashed, draw=purple!60!white] table [x=pO2, y=Ii{1},]{dat/1e5iconctet1500.dat}; \addlegendentry{\ch{I_{i}^{\textperiodcentered}}};

@@

        \addplot[no marks, dashed, draw=green!60!black] table [x=pO2, y=IsubO{2},]{dat/1e5iconctet1500.dat}; \addlegendentry{\ch{I_{O}^{\textperiodcentered\textperiodcentered}}};
        \addplot[no marks, dashed, draw=black] table [x=pO2, y=IsubO{3},]{dat/1e5iconctet1500.dat}; \addlegendentry{\ch{I_{O}^{\textperiodcentered\textperiodcentered\textperiodcentered}}};

@@

        \addplot[no marks, dashed, draw=purple!60!white] table [x=pO2, y=Ii{1},]{dat/1e3iconctet1500.dat}; 

@@

        \addplot[no marks, dashed, draw=green!60!black] table [x=pO2, y=IsubO{2},]{dat/1e3iconctet1500.dat}; 
        \addplot[no marks, dashed, draw=black] table [x=pO2, y=IsubO{3},]{dat/1e3iconctet1500.dat}; 

@@

		\caption{Tetragonal phase Brouwer diagrams of point defects at iodine concentrations of a) $10^{-5}$ and b) $10^{-3}$, at a temperature of 1500 K.}

@@

		[width=8.22cm, xlabel={\ch{log_{10}}($p_{O_{2}}$) (atm)}, ylabel={\ch{log_{10}}([D]) (per f.u.)}, ymin=-10, ymax=0, xmin=-35, xmax=0, legend style={{draw=}, at={(0.30,1.47)}, anchor=north west, legend columns=3, nodes={scale=0.75, transform shape}}]

@@

         \addplot[no marks, draw=yellow!75!blue] table [x=pO2, y=VM{-3},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{V_{Zr}^{'''}}};

@@

         \addplot[no marks, draw=red!60!yellow] table [x=pO2, y=Oi{-2},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{O_{i}^{''}}};

@@

         \addplot[no marks, dashed, draw=red!70!black] table [x=pO2, y=Xei{0},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{Xe_{i}^{x}}};
         \addplot[no marks, dashed, draw=red!50!black] table [x=pO2, y=Xei{-1},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{Xe_{i}^{'}}};
        \addplot[no marks, dashed, draw=purple] table [x=pO2, y=Xei{1},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{Xe_{i}^{\textperiodcentered}}};
        \addplot[no marks, dashed, draw=blue!50!white] table [x=pO2, y=XesubO{1},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{Xe_{O}^{\textperiodcentered}}};

@@

        \addplot[no marks, dashed, draw=red!70!black] table [x=pO2, y=Xei{0},]{dat/xe_tet_10-3.dat}; 
        \addplot[no marks, dashed, draw=red!50!black] table [x=pO2, y=Xei{-1},]{dat/xe_tet_10-3.dat}; 
        \addplot[no marks, dashed, draw=purple] table [x=pO2, y=Xei{1},]{dat/xe_tet_10-3.dat}; 
        \addplot[no marks, dashed, draw=blue!50!white] table [x=pO2, y=XesubO{1},]{dat/xe_tet_10-3.dat}; %\node at (-11,-2.6) {\ch{I_{O}^{\textperiodcentered}}};

@@

		\caption{Tetragonal phase Brouwer diagrams of point defects at Xenon concentrations of a) $10^{-5}$ and b) $10^{-3}$, at a temperature of 1500 K. Space charge = 0}

@@

		[width=8.22cm, xlabel={\ch{log_{10}}($p_{O_{2}}$) (atm)}, ylabel={\ch{log_{10}}([D]) (per f.u.)}, ymin=-10, ymax=0, xmin=-35, xmax=0, legend style={{draw=}, at={(0.30,1.47)}, anchor=north west, legend columns=3, nodes={scale=0.75, transform shape}}]

@@

         \addplot[no marks, dashed, draw=red!70!black] table [x=pO2, y=Csi{0},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{Cs_{i}^{x}}};
         \addplot[no marks, dashed, draw=red!50!black] table [x=pO2, y=Csi{-1},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{Cs_{i}^{'}}};
        \addplot[no marks, dashed, draw=purple] table [x=pO2, y=Csi{1},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{Cs_{i}^{\textperiodcentered}}};
        \addplot[no marks, dashed, draw=blue!50!white] table [x=pO2, y=CssubO{1},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{Cs_{O}^{\textperiodcentered}}};

@@

        \addplot[no marks, dashed, draw=red!70!black] table [x=pO2, y=Csi{0},]{dat/cs_tet_10-3.dat}; 

>>>>

Nuclear fuel claddings have unique materials challenges owing to the highly active environment in which they operate and the creation of unstable isotopes. Corrosive species in the pin such as iodine, produced directly as a result of uranium fission are known to play a role in SCC \cite{Sidky1998, Fregonese1998, iodinezrmetal}. However, iodine nuclei produced from fission are unstable. Fission of uranium produces iodine precursors, mainly unstable isotopes of tellurium. Both iodine and tellurium are relatively common fission products, with combined independent yields from thermal fission of U$_{235}$ of more than 5\% \cite{kennett1956mass, iodine129fissionyield, imanishi1976independent, iaeafissionyield, iodine132, amiel1975odd}. In addition, xenon and caesium are also common fission products, as shown in Figure \ref{fig:fissionyield}, with fission product masses firmly within the heavy nuclide peak of uranium and plutonium fission product distribution curves.    \\

Previous work on defect equilibria in \zirconia\ considered the internal side of the fuel cladding oxide layer's effectiveness as a barrier to iodine \cite{kenichiodine2018}. It was found that the tetragonal phase of \zirconia\ is a better barrier to iodine ingress than monoclinic \zirconia , especially at higher oxygen partial pressures. It is also established that tetragonal \zirconia\ will always be present on the inner surface of the cladding in significant quantities because it is self-stabilised by the stresses imposed as the oxide grows into the zirconium metal, in addition to compressive residual stresses induced by radiation damage \cite{causey2005review}. The iodine defect study, however, only informs us about one part of the SCC process. For a more holistic understanding, the life cycle of the iodine must also be taken into account.     \\

@@

Nuclei produced during fission are typically neutron-rich, resulting in decay modes such as $\beta-$ or neutron emission. In the case of tellurium nuclei, most decay into iodine, which then decays into xenon with different half-lives depending on the isotope. An example of such a decay chain is shown in Figure \ref{fig:decaychain} using Te$_{135}$. Several of these isotopes' fission yield and decay data are shown in Table \ref{table:decaydata}. The decay chain continues with xenon nuclei decaying into caesium, many isotopes of which have half lives measured in years. At this point, conventional power reactor fuel is retired long before a significant proportion of the caesium decays into barium. For this reason we only consider the elements tellurium through caesium in this study. \\

A large fraction of thermal fission events occur in the outer rim of a fuel pellet. Given a fission product penetration depth of up to 8 $\mu$m in \zirconia\ \cite{degueldre2001behaviour}, a large proportion of fission products implant within the oxide. It has also been observed in PCI failures that there is a time delay on the order of 10 minutes between the power ramping of the reactor and the subsequent breach of the cladding \cite{bergenlid1980experimental, wood1983effects, pankaskie1981mechanistic}. This time delay is in line with the half-lives of many Te and I isotopes (Table \ref{table:decaydata}) such that significant proportions of these isotopes will decay during this time delay, hinting that these phenomena could be related. \\
%In addition, it is known that irradiated cladding containing fresh fuel does not crack when power ramped  \cite{wood1983effects}. \\

@@

Calculations were performed using the CASTEP 8.0 density functional theory (DFT) based code \cite{Clark2005}. Ultra-soft pseudo-potentials with a cut-off energy of 600 eV were employed. The exchange correlation functional was described by the Perdew, Burke and Ernzerhof (PBE) \cite{Perdew1996} parameterisation of the generalised gradient approximation (GGA). A Monkhorst-Pack sampling scheme \cite{Monkhorst1976} was used for Brillouin zone integration, with a minimum \emph{k}-point separation of 0.09 \r{A}\textsuperscript{-1}. The Pulay method for density mixing \cite{Pulay1980} was used to improve simulation convergence. \\

@@

Tellurium on an oxygen site adopts a 0 charge state, which while not obvious (it may be expected to act like oxygen, also a group 6 element), can be understood when considering chemical behaviour. Oxygen on its native site will readily adopt a charge state of -2. Tellurium on the other hand, exhibits more metallic behaviour, preferring to be oxidised itself (the electronegativities of oxygen and tellurium are 3.5 and 2.1 respectively). However, the \ch{V_{O}^{**}} site is highly reducing, and will counter the tellurium ion's proclivity to oxidise. The overall effect on tellurium in this case is to maintain its original electronic structure. Finally, when the tellurium concentration is increased to $10^{-3}$ parts/fu, greater occupancy on the zirconium site is predicted above oxygen pressures of $10^{-17}$ atm, forming the defect \ch{Te_{Zr}^{'''}}. This corresponds to a tellurium charge state of +1. While we would expect an even more positive charge state for tellurium, in this case it is the dominant negative defect by an order of magnitude and is necessary to charge compensate positive hole and \ch{Te_{O}^{**}} defects. \\

The presence of these defects and their sizes will have an effect on the lattice, particularly if there is a lattice mismatch which results in a significant local strain. In terms of defect volume, \ch{Te_{O}^{**}} has a slightly positive volume of 2.74 \r{A}$^{3}$ relative to the non-defective crystal. This is quite large for a positively charged defect (\ch{V_{O}^{**}} has a defect volume of -40.45 \r{A}$^{3}$), very likely due to the large size of the tellurium atom itself. When tellurium occupies the zirconium site, the resulting \ch{Te_{Zr}^{'''}} has a defect volume of 59.93 \r{A}$^{3}$. While this is lower than the defect volume of \ch{V_{Zr}^{''''}} (88.93 \r{A}$^{3}$), it is still an increase in volume relative to the non-defective crystal and will impart a strain on the lattice which, at a high enough defect concentration, could contribute to crack formation.

@@

Iodine was previously predicted in Brouwer diagrams (Figure \ref{figure:tikzbrouwerconctet} to produce the defects \ch{I_{O}^{*}} and \ch{I_{Zr}^{'''}} at low and high oxygen pressures respectively. Since the extrinsic defect site is similar for tellurium defects over most oxygen pressures, $\beta$- decay of tellurium could have directly produced these iodine defects without requiring a change of site. Thus, \ch{Te_{O}^{**}} would decay and produce \ch{I_{O}^{*}} with a defect volume of 29.90 \r{A}$^{3}$, and \ch{Te_{Zr}^{'''}} would decay and produce \ch{I_{Zr}^{'''}} with a defect volume of 87.07 \r{A}$^{3}$. At the oxygen site, this means a defect volume increase from 2.74 to 29.90 \r{A}$^{3}$. This increase is in large part due to the change in charge state from 0 to -1, as the ions are of similar size otherwise. \\

Similarly at the zirconium site, the defect volume increases from 59.93 to 87.07 \r{A}$^{3}$. Both decays of Te to I produce relatively large increases in defect volume and will come with an increase in lattice stress in the immediate vicinity of the defect, especially if highly constrained. Of course, this  process will take place continuously over time as tellurium atoms decay, with half-lives ranging from seconds to hours depending on the isotope. It is of note however, that PCI failures tend to occur after power ramps with a time delay, even up to an hour after the transient. While not conclusive, this may hint at a mechanism involving decay processes.

@@

Brouwer diagrams for xenon defects are shown in Figure \ref{figure:xenonbrouwer}. At a xenon concentration of $10^{-5}$ parts/fu \zirconia , the dominant xenon defect is \ch{Xe_{O}^{**}} at low oxygen pressures, and a combination of \ch{Xe_{O}^{**}}, \ch{Xe_{Zr}^{''''}} and \ch{Xe_{Zr}^{'''}} at stoichiometry ($10^{-9}$ atm) and higher. At a higher xenon concentration of $10^{-3}$ parts/fu \zirconia , \ch{Xe_{O}^{**}} becomes the dominant defect over a greater oxygen pressure range, from $10^{-30}$ to $10^{-5}$ atm, with \ch{Xe_{Zr}^{''''}} also present in high concentrations at oxygen pressures above $10^{-20}$ atm. As a noble gas, it is expected that xenon in a 0 charge state (\ch{Xe_{O}^{**}} and \ch{Xe_{Zr}^{''''}}) will be prevalent since its highly stable electronic configuration makes it chemically inert (large energy costs associated with adding or removing valence electrons). \\

@@

The defect volumes of \ch{Cs_{O}^{**}} and \ch{Cs_{Zr}^{'''}} were 4.38 and 90.37 \r{A}$^{3}$ respectively, less than the Xe defects on the same site. This is consistent with the fact that Cs has a much smaller first ionisation energy than Xe, therefore presenting a smaller energy barrier to reducing its size on either site to improve lattice fit. Because of this, we do not expect further stresses being imposed on the lattice after Xe decays to Cs. We therefore consider that only Te, I and Xe will be significant in this mechanism, as the only contribution to lattice stresses due to Cs would have occurred through direct implantation after fission.

@@

As fission products proceed down the decay chain from Te to Xe, the defects they produce in \zirconia\ have progressively larger volumes. The change in defect volume when \ch{Te_{Zr}^{'''}} decays and produces \ch{I_{Zr}^{'''}} is +27.14 \r{A}$^{3}$. This then decays and produces the defect \ch{Xe_{Zr}^{''''}}, which leads to an even larger change in defect volume of +28.43 \r{A}$^{3}$. Similarly, at the oxygen site, \ch{Te_{O}^{**}} decays to produce \ch{I_{O}^{*}}, with a resulting defect volume change of +27.16 \r{A}$^{3}$. The lattice mismatch of these defects in \zirconia\ will generate stresses and if produced in significant quantities could promote crack formation, exposing Zr metal. If enough fission products are implanted simultaneously, the rate of crack formation may become faster than new passivating oxide can be produced, and typical I-SCC mechanisms will take over to failure. This process may be a contributing factor to fuel cladding failures observed after a power ramp, with reported time delays between ramp and failure aligning with the decay rate of Te and I isotopes.

@@

\begin{figure}
    \centering
    \includegraphics[height=8cm]{img/te_decay_chain.png}
    \caption{Diagram of the Te$_{135}$ decay chain with decay modes and half-lives shown.}
    \label{fig:decaychain}
\end{figure}

@@

		[width=8.22cm, xlabel={\ch{log_{10}}($p_{O_{2}}$) (atm)}, ylabel={\ch{log_{10}}([D]) (per f.u.)}, ymin=-10, ymax=0, xmin=-35, xmax=0, legend style={{draw=}, at={(0.37,0.965)}, anchor=north west, legend columns=3, nodes={scale=0.75, transform shape}}]

@@

         %\addplot[no marks, draw=yellow!75!blue] table [x=pO2, y=VM{-3},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{V_{Zr}^{'''}}};

@@

         %\addplot[no marks, draw=red!60!yellow] table [x=pO2, y=Oi{-2},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{O_{i}^{''}}};
         %\addplot[no marks, draw=red!50!yellow] table [x=pO2, y=Oi{-1},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{O_{i}^{'}}};
         %\addplot[no marks, draw=red!40!yellow] table [x=pO2, y=Oi{0},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{O_{i}^{x}}};

@@

         %\addplot[no marks, dashed, draw=red!70!black] table [x=pO2, y=Tei{0},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{Te_{i}^{x}}};
         %\addplot[no marks, dashed, draw=red!50!black] table [x=pO2, y=Tei{-1},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{Te_{i}^{'}}};
        %\addplot[no marks, dashed, draw=purple] table [x=pO2, y=Tei{1},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{Te_{i}^{\textperiodcentered}}};

@@

        %\addplot[no marks, dashed, draw=black] table [x=pO2, y=TesubO{3},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{Te_{O}^{\textperiodcentered\textperiodcentered\textperiodcentered}}};

@@

         %\addplot[no marks, dashed, draw=pink] table [x=pO2, y=TesubZr{-4},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{Te_{Zr}^{''''}}};
         %\addplot[no marks, dashed, draw=purple] table [x=pO2, y=TesubZr{-5},]{dat/te_tet_10-5.dat}; \addlegendentry{\ch{Te_{Zr}^{'''''}}};

@@

        %\addplot[no marks, dashed, draw=red!70!black] table [x=pO2, y=Tei{0},]{dat/te_tet_10-3.dat}; 
        %\addplot[no marks, dashed, draw=red!50!black] table [x=pO2, y=Tei{-1},]{dat/te_tet_10-3.dat}; 
        %\addplot[no marks, dashed, draw=purple] table [x=pO2, y=Tei{1},]{dat/te_tet_10-3.dat}; 

@@

        %\addplot[no marks, dashed, draw=black] table [x=pO2, y=TesubO{3},]{dat/te_tet_10-3.dat}; 

@@

        %\addplot[no marks, dashed, draw=pink] table [x=pO2, y=TesubZr{-4},]{dat/te_tet_10-3.dat}; 
        %\addplot[no marks, dashed, draw=purple] table [x=pO2, y=TesubZr{-5},]{dat/te_tet_10-3.dat}; 

@@

		\caption{Brouwer diagrams for tetragonal phase \zirconia\ point defects at tellurium concentrations of a) $10^{-5}$ and b) $10^{-3}$, at a temperature of 1500 K.} % Space charge = 0

@@

        %\addplot[no marks, dashed, draw=purple!60!white] table [x=pO2, y=Ii{1},]{dat/1e5iconctet1500.dat}; \addlegendentry{\ch{I_{i}^{\textperiodcentered}}};

@@

        %\addplot[no marks, dashed, draw=green!60!black] table [x=pO2, y=IsubO{2},]{dat/1e5iconctet1500.dat}; \addlegendentry{\ch{I_{O}^{\textperiodcentered\textperiodcentered}}};
        %\addplot[no marks, dashed, draw=black] table [x=pO2, y=IsubO{3},]{dat/1e5iconctet1500.dat}; \addlegendentry{\ch{I_{O}^{\textperiodcentered\textperiodcentered\textperiodcentered}}};

@@

        %\addplot[no marks, dashed, draw=purple!60!white] table [x=pO2, y=Ii{1},]{dat/1e3iconctet1500.dat}; 

@@

        %\addplot[no marks, dashed, draw=green!60!black] table [x=pO2, y=IsubO{2},]{dat/1e3iconctet1500.dat}; 
        %\addplot[no marks, dashed, draw=black] table [x=pO2, y=IsubO{3},]{dat/1e3iconctet1500.dat}; 

@@

		\caption{Brouwer diagrams for tetragonal phase \zirconia\ point defects at iodine concentrations of a) $10^{-5}$ and b) $10^{-3}$, at a temperature of 1500 K.}

@@

		[width=8.22cm, xlabel={\ch{log_{10}}($p_{O_{2}}$) (atm)}, ylabel={\ch{log_{10}}([D]) (per f.u.)}, ymin=-10, ymax=0, xmin=-35, xmax=0, legend style={{draw=}, at={(0.35,0.97)}, anchor=north west, legend columns=3, nodes={scale=0.75, transform shape}}]

@@

         %\addplot[no marks, draw=yellow!75!blue] table [x=pO2, y=VM{-3},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{V_{Zr}^{'''}}};

@@

         %\addplot[no marks, draw=red!60!yellow] table [x=pO2, y=Oi{-2},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{O_{i}^{''}}};

@@

        %\addplot[no marks, dashed, draw=red!70!black] table [x=pO2, y=Xei{0},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{Xe_{i}^{x}}};
        %\addplot[no marks, dashed, draw=red!50!black] table [x=pO2, y=Xei{-1},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{Xe_{i}^{'}}};
        %\addplot[no marks, dashed, draw=purple] table [x=pO2, y=Xei{1},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{Xe_{i}^{\textperiodcentered}}};
        %\addplot[no marks, dashed, draw=blue!50!white] table [x=pO2, y=XesubO{1},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{Xe_{O}^{\textperiodcentered}}};

@@

        %\addplot[no marks, dashed, draw=red!70!black] table [x=pO2, y=Xei{0},]{dat/xe_tet_10-3.dat}; 
        %\addplot[no marks, dashed, draw=red!50!black] table [x=pO2, y=Xei{-1},]{dat/xe_tet_10-3.dat}; 
        %\addplot[no marks, dashed, draw=purple] table [x=pO2, y=Xei{1},]{dat/xe_tet_10-3.dat}; 
        %\addplot[no marks, dashed, draw=blue!50!white] table [x=pO2, y=XesubO{1},]{dat/xe_tet_10-3.dat}; %\node at (-11,-2.6) {\ch{I_{O}^{\textperiodcentered}}};

@@

		\caption{Brouwer diagrams for tetragonal phase \zirconia\ point defects at Xenon concentrations of a) $10^{-5}$ and b) $10^{-3}$, at a temperature of 1500 K.}% Space charge = 0}

@@

		[width=8.22cm, xlabel={\ch{log_{10}}($p_{O_{2}}$) (atm)}, ylabel={\ch{log_{10}}([D]) (per f.u.)}, ymin=-10, ymax=0, xmin=-35, xmax=0, legend style={{draw=}, at={(0.37,0.97)}, anchor=north west, legend columns=3, nodes={scale=0.75, transform shape}}]

@@

         %\addplot[no marks, dashed, draw=red!70!black] table [x=pO2, y=Csi{0},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{Cs_{i}^{x}}};
         %\addplot[no marks, dashed, draw=red!50!black] table [x=pO2, y=Csi{-1},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{Cs_{i}^{'}}};
        %\addplot[no marks, dashed, draw=purple] table [x=pO2, y=Csi{1},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{Cs_{i}^{\textperiodcentered}}};
        %\addplot[no marks, dashed, draw=blue!50!white] table [x=pO2, y=CssubO{1},]{dat/cs_tet_10-5.dat}; \addlegendentry{\ch{Cs_{O}^{\textperiodcentered}}};

@@

        %\addplot[no marks, dashed, draw=red!70!black] table [x=pO2, y=Csi{0},]{dat/cs_tet_10-3.dat}; 
